### 2021-01-28 msc-thesis.tex
Corrections

The goal of the integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. The main OZG functionalities are:
\begin{enumerate}
    \item{Create User Profile}
    \item{Login to User Profile}
    \item{Selection of Administrative Service}
    \item{Filling in Application}
    \item{Submission of Application}
    \item{Reception of Application by Administration Portal}
    \item{Submission of Application to Data-Exchange Platform}
    \item{Management of Applications}
    \item{Communication}
\end{enumerate}

@@

\section{Integration Architecture 1}

Integrating an IMP solution for management of customer identities is no simple task. To make the introduction of IMP systems easier for service providers, this first integration architecture describes a non invasive integration. After applying this integration, all OZG services are still usable as before but can be enhanced by IMP solutions. For this integration not to be invasive, only one connector exists and integrates only with the administration portal. No other OZG system component is modified or directly accessed.

@@

It would be possible to integrate the IMP identity as an alternative to the user profile. The user could then use OZG services either by creating a user profile or by providing an IMP identity. Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile. The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management. The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution. OZG systems would have to request personal information from the IMP identity while providing a reason for doing so. After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity. However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile. As the focus of this integration architecture is simplicity and non incisiveness, the connection of IMP identity and user profile is preferred.

@@

The IMP connector provides an API for creation of relationship templates as part of its REST interface. Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response. The web page can then render the template as a QR code on the web page.

@@

Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request. If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request. The server would have to regularly request a status update which is not efficient. Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified. The administration portal can process the relationship request and publish a message containing a response on the "Relationship Request Response" channel, where the connector will be notified. Through the IMP server, the connector sends the response to the IMP client and the relationship is established.
In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.

@@

Neues Kapitel/Überschrift: Attribute Synchronization

@@

The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically. However, this would require the user to always share the most current personal information with the OZG systems. Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider. If the user for example changes the home address of its IMP identity, the OZG system might not want to approve this change immediately. If the user manages IMP identity and user profile separately, changes of the OZG user profile can happen on a request reply basis. The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there. The disadvantage of this option is, that the management of personal information is more complicated than the first option. Through attribute management tools on the IMP client, the experience can be improved.

@@

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal. As the integration solution for connection of user profile and IMP identity was chosen, the user is still able to login to his user profile on the administration portal and take advantage of all OZG services. The IMP system can however provide an additional way to access OZG services through the IMP client. One possibility was already introduced: the management of personal information.

In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid. Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session. When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components. This process is necessary because any person can send requests to the web server and possibly pretend to be a different user. In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user. Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity. As the IMP client is an app installed on the smartphone of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.

>>>>

The goal of the integration architecture is to make as many functionalities required for the basic OZG use case available through the IMP client as possible. As described in chapter 2.3, the steps of the basic OZG use case are:
\begin{enumerate}
    \item{Create User Profile}
    \item{Login to User Profile}
    \item{Selection of Administrative Service}
    \item{Filling in Application}
    \item{Submission of Application}
    \item{Reception of Application by Administration Portal}
    \item{Submission of Application to Data-Exchange Platform}
    \item{Management of Applications}
    \item{Communication}
\end{enumerate}

@@

\section{Minimal Integration Architecture}
To enable service providers a quick introduction of IMP systems into their system architecture, this first integration architecture describes a minimally invasive integration. After deployment of this integration architecture, all OZG services are still usable as before but can be enhanced by IMP solutions. For this integration to be minimally invasive, only one connector exists and integrates only with the administration portal. No other OZG system component is modified or directly accessed.

@@

It would be possible to integrate the IMP identity as an alternative to the user profile. The user could then use OZG services either by creating an OZG user profile or by providing an IMP identity. Another option would be to enable a connection of an existing IMP identity and an existing OZG user profile. The user would then have to create a user profile in order to access OZG services but could connect an IMP identity for improved identity management. The benefit of using the IMP identity as an alternative is, that the user has better control over his personal information, as the attributes of the identity are not stored by the OZG system architecture but the IMP solution. OZG systems would have to request personal information from the IMP identity while providing a reason for doing so. After the user updates attributes of its IMP identity, the OZG systems would automatically use the most recent values when requesting access to personal information of the IMP identity. However, this form of integration is already pretty advanced and would require invasive integration in order for the administration portal to add an additional process for executing the basic use case with the IMP identity instead of the user profile. As the focus of this integration architecture is non invasiveness, the connection of IMP identity and user profile is preferred.

@@

The IMP connector provides an API for creation of relationship templates as part of its REST interface. Through a HTTP POST call, the web server transmits the appropriate request to the connector and receives the template as response. The web page of the administration portal can then render the template as a QR code on the web page.

@@

Upon receiving the request, the connector has to notify the administration portal of an incoming relationship request. If the web server does not provide an HTTP endpoint for communicating with the connector, it won't be able to receive a notification about the arrival of a new relationship request. The server would have to regularly request a status update which is not efficient. Using messaging, the connector can publish the content of the relationship request to a "Relationship Request" channel where the subscribed administration portal will be notified. The administration portal can process the relationship request and publish a message containing a response on the "Relationship Response" channel, where the connector will be notified. Through the IMP server, the response server is routed to the IMP client and the relationship is established.
In order to map relationships to user profiles, the administration portal manages a database which contains entries consisting of IMP identity ID, relationship ID and user profile ID.

@@

\paragraph{Attribute Synchronization}

@@

The benefit of the first option is, that the user only has to manage attributes for his IMP identity and the user profile will be updated automatically. However, this would require the user to always share the most current personal information with the OZG systems. Depending on the service provider, updates of attributes might not be possible in every case or would require additional actions by the service provider. If the user for example changes the birth date of its IMP identity, the OZG system might not want to approve this change immediately. Another option would be for the user to manage IMP identity and user profile separately. Changes of the OZG user profile can then happen on a request reply basis. The user would also be able to manage its OZG user profile through the web page of the administration portal and request attribute changes from there. The disadvantage of this option is, that the management of personal information is more complicated than the first option. Through attribute management tools on the IMP client, the experience can be improved.

@@

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal to access OZG services. As previously described, the integration architecture does not replace the OZG user profile. The user is therefore still able to login to his user profile on the administration portal and take advantage of all OZG services. The IMP system can however provide an additional way to access OZG services through the IMP client. One possibility was already introduced: the management of personal information.

In order for the administration portal to perform actions on behalf of a user, it has to verify, that the request is valid. Through the web page, this is often done by establishing a browser session, through a cookie and after the authentication process, updating the authentication status of the session. When the web server receives a request from a authenticated session, it can use a JSON Web Token, created during the registration process to access resources of other system components. This process is necessary because any person can send requests to the web server and possibly pretend to be a different user. In contrast to the web browser, requests coming through the IMP system can be assumed to be valid and therefore originate from the correct IMP identity and user. Therefore it is not necessary for the user to authenticate for the OZG system when using an IMP identity. As the IMP client is an app installed on the device of the user, it might even be possible to completely remove user authentication when accessing the client as most users secure their phones through a lock pattern already.
